### 2014-03-12 src/analysis.Rnw
update

\section{Analysis}
\label{sec:analysis}
Our results for x\% sampling over program elements are given
in Table~\ref{tbl:xselsample}. The result of its variation, using
\textit{round(sample)} is given in Table~\ref{tbl:xselround}. The result
of using \textit{ceil(sample)} is given in Table~\ref{tbl:xselceil}.
The first column in each table provides the scope of sampling i.e if it was
done per class, per method, per line etc. The second column provides the
fraction involved.  Third column contains the $R^2$ value obtained between
the mutation score of the sampling criteria used and the full mutation score.
The fourth column contains the mutant reduction factor. This is the average of
total mutants produced divided by the number of mutants sampled by the criteria.
Fifth column contains the standard deviation of the same. A few of the projects
did not return any value for certain sampling criterias for particular mutation
reduction fractions. The sixth column contains the number of projects that
actually had valid values for the criteria being considered. The seventh column
is the average multiplier between the sampled mutation score and the full mutation
score.

@@

\begin{figure*}[t]
<<x.per.sel.sample,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
o.xp <- subset(o.processed, grepl('^rr[.].*.m[.]red',ind))
ggplot(subset(o.xp, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
  stat_boxplot(geom ='errorbar')+
  geom_boxplot() + facet_wrap(~type) + myopts
@
\caption{The effect of sample(x) reduction. All are above 0.90 $R^2$.}
\label{fig:xsamplesel}
\end{figure*}
%TODO : See if the following paragraph is needed, or shall we just sink the ceil(x) discussion completely?
Our experiments found that while $round(x)$ and $sample(x)$ produced relatively reasonable reduction of mutants, the $ceil(x)$ criteria failed to produce a reasonable reduction of mutants except for higher power where the reduction was some what close to that produced by $round(x)$ and $sample(x)$ (which was expected). The $R^2$ values of $ceil(x)$ were almost always lower than that produced by $round(x)$ and $sample(x)$ for similar reduction of mutants. For this reason, we do not consider this function again. However, interested parties can refer to our published data.

The reduction in mutants for x\% selection using $round(x)$ is graphed in Figure~\ref{fig:xroundsel}. The values for the same are given in Table~\ref{tbl:xsel}.
Similarly reduction in mutants for x\% selection using $sample(x)$ is graphed in Figure~\ref{fig:xsamplesel}. The values for the same are given in Table~\ref{tbl:xsel}.
% ----------------------------------------------------------------------

>>>>

\section{Analysis}
\label{sec:analysis}
For the purposes of comparing between the criterias, we computed the
correlation between sampled mutation score and full mutation score.
Since for most of the sampling criteria, if there are no mutants to
sample, it probably means there are no mutants generated on the whole,
we used $lm(M_{all}~0+M_{sample})$ as the regression formula, and report
the correlation from this linear regression. We also report the expected
multiplier factor for the sampled mutation score. This factor determines
the ease of satisfying the sampling criteria. That is, if the multiplier
factor is small, then it is easier to satisfy compared to a larger multiplier
factor.
Next, for each criteria, we computed the reduction of mutants given by the
ratio between total number of mutants and sampled mutants.
We also compute standard deviation of the mutant reduction, which determines
the consistency of results. (A large amount of standard deviation suggests
that the mutant reduction ratio achieved is very much dependent on the
project. So as a heuristic, we suggest looking at only those projects which
has a mean reduction ratio atleast twice the standard deviation.)

For some of the smaller projects, some of the sampling criteria did not
return any results. This is also collected in our tables.

@@

\begin{figure*}[t]
<<x.per.sel.sample,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
o.xp <- subset(o.processed, grepl('^rr[.].*.m[.]red',ind))
ggplot(subset(o.xp, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
  stat_boxplot(geom ='errorbar')+
  geom_boxplot() + facet_wrap(~type) + myopts
@
\caption{The effect of sample(x) reduction. All are above 0.90 $R^2$.}
\label{fig:xsamplesel}
\end{figure*}
%TODO : See if the following paragraph is needed, or shall we just sink the ceil(x) discussion completely?
Our experiments found that while $round(x)$ and $sample(x)$ produced relatively reasonable reduction of mutants, the $ceil(x)$ criteria failed to produce a reasonable reduction of mutants except for higher power where the reduction was some what close to that produced by $round(x)$ and $sample(x)$ (which was expected). The $R^2$ values of $ceil(x)$ were almost always lower than that produced by $round(x)$ and $sample(x)$ for similar reduction of mutants. For this reason, we do not consider this function again. However, interested parties can refer to our published data.
% ----------------------------------------------------------------------

### 2014-03-12 src/results.Rnw
update

\section{Results}
\label{sec:results}
\subsection{Standard deviation of mutant reduction}
We observe multiple patterns in our results. First, for all sampling criterias used, standard deviation of reduction of mutants is roughly proportional to their mean value. This can be seen in Figure~\ref{fig:roundsel}. Secondly, we also observe that standard deviation based on project sampling is lower than standard deviation of class based sampling for corresponding mean mutant reduction, and the standard deviation of class based sampling is lower than that based on methods, and similarly for lines.

>>>>

\section{Results}
\label{sec:results}

Our results for x\% sampling over program elements are given
in Table~\ref{tbl:xselsample}. The result of its variation, using
\textit{round(sample)} is given in Table~\ref{tbl:xselround}. The result
of using \textit{ceil(sample)} is given in Table~\ref{tbl:xselceil}.
The first column in each table provides the scope of sampling i.e if it was
done per class, per method, per line etc. The second column provides the
fraction involved.  Third column contains the $R^2$ value obtained between
the mutation score of the sampling criteria used and the full mutation score.
The fourth column contains the mutant reduction factor. This is the average of
total mutants produced divided by the number of mutants sampled by the criteria.
Fifth column contains the standard deviation of the same. A few of the projects
did not return any value for certain sampling criterias for particular mutation
reduction fractions. The sixth column contains the number of projects that
actually had valid values for the criteria being considered. The seventh column
is the average multiplier between the sampled mutation score and the full mutation
score.

\subsection{Standard deviation of mutant reduction}
We observe multiple patterns in our results. First, for all sampling criterias used, standard deviation of reduction of mutants is roughly proportional to their mean value. This can be seen in Figure~\ref{fig:roundsel}. Secondly, we also observe that standard deviation based on project sampling is lower than standard deviation of class based sampling for corresponding mean mutant reduction, and the standard deviation of class based sampling is lower than that based on methods, and similarly for lines.
